The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-02-11 papers/pair-correlation/paper.tex
incomplete changes from meeting with Jeff (see paper for reasoning) Tested on node23. Took 29:35.78.

We construct $g(r, g_\sigma)$ to satisfy several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
A second constraint applies to the integral of the total correlation
function
\begin{align}
  1 + n\int h(r)d\rr &= nkT\chi_T \label{eq:total-constraint}
\end{align}
where $h(r) = g(r) - 1$ is the total correlation function.
A final constraint is that the slope of the radial distribution
function at contact is given to a very good approximation by \fixme{fix dimensions below}
\begin{align}
  g'(\sigma) \approx - h_\sigma g_\sigma
\end{align}
where $h_\sigma = g_\sigma - 1$ is the total correlation function.
Under these three constraints, we applied a least-squares fit to
simulation data for the radial distribution function at packing
fractions from 0.05 to 0.4 by steps of 0.05.  Our fitted radial
distribution function is given by
\newcommand\kappaa{\kappa_0}
\newcommand\kappab{\kappa_1}
\newcommand\kappac{\kappa_2}
\begin{multline}
  h(r,g_\sigma) = 1 + h_\sigma e^{-\kappaa z} \\
  + h_\sigma(\kappaa - g_\sigma) ze^{-\kappab z} \\
  + \frac{\frac{(1-\eta)^4}{1+4\eta + 4\eta^2 - 4\eta^3 +
      \eta^4}\frac{1}{n}
    - I_0  -I_1(\kappaa - g_\sigma)}{I_2} z^2e^{-\kappac z}
\end{multline}
\begin{equation}
  I_0 = \frac{4\pi h_\sigma (2 + \sigma \kappaa (2 + \sigma \kappaa))}{\kappaa^3}
  - \frac{4\pi}{3} \sigma^3
\end{equation}
\begin{equation}
  I_1 = \frac{4\pi h_\sigma (6 + \sigma \kappab (4 + \sigma \kappab))}{\kappab^4}
\end{equation}
\begin{equation}
  I_2 = \frac{8\pi (12 + \sigma \kappac (6 + \sigma \kappac))}{\kappac^5}
\end{equation}
\begin{equation}
  z = r - \sigma
\end{equation}
\davidsays{Can someone check the above equations for correctness
  against the python code, in plot-ghs2.py.  We'll want to
  ensure the C++ code agrees with this as well.}
\fixme{Clean up the above equations, if possible.}
This function includes three fitted parameters, $\kappaa$, $\kappab$,
and $\kappac$, which are given in Table~\ref{tab:fit-parameters}.
The fit is displayed in Fig.~\ref{fig:radial-distribution}.  In that
figure, it is apparent that the integral f $h(r)$ from
Eq.~\ref{eq:total-constraint} results in cancelling errors at large
distances.  The maximum error in $g(r)$ at packing fractions up to
0.4 is \maxerr, which occurs at $\eta = \etamaxerr$ and $r =
\rmaxerr$.

\begin{table}
  \begin{tabular}{cc}
    $\kappaa$ & \kappazero \\
    $\kappab$ & \kappaone \\
    $\kappac$ & \kappatwo
  \end{tabular}
  \caption{Fit parameters \fixme{... put them here and format this nicely}\fixme{add dimensions here}}
  \label{tab:fit-parameters}
\end{table}

>>>>

We construct $g(r, g_\sigma)$ to satisfy several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
A second constraint applies to the integral of the total correlation
function
\begin{align}
  1 + n\int h(r)d\rr &= nkT\chi_T \label{eq:total-constraint}
\end{align}
where $h(r) = g(r) - 1$ is the total correlation function.
A final constraint is that the slope of the radial distribution
function at contact is given to a very good approximation by \fixme{fix dimensions below}
\begin{align}
  g'(\sigma) \approx - h_\sigma g_\sigma
\end{align}
where $h_\sigma = g_\sigma - 1$ is the total correlation function.
Under these three constraints, we applied a least-squares fit to
simulation data for the radial distribution function at packing
fractions from 0.05 to 0.4 by steps of 0.05.  Our fitted radial
distribution function is given by
\newcommand\kappaO{c_0}
\newcommand\kappaI{c_1}
\newcommand\kappaZ{c_2}
\begin{multline}
  g(r,g_\sigma) = 1 + h_\sigma e^{-\kappaO \left(\frac{r}{\sigma}-1\right)} \\
  + h_\sigma(\kappaO - g_\sigma)  \left(\frac{r}{\sigma}-1\right)e^{-\kappaI  \left(\frac{r}{\sigma}-1\right)} \\
  + B  \left(\frac{r}{\sigma}-1\right)^2e^{-\kappaZ  \left(\frac{r}{\sigma}-1\right)}
\end{multline}
\begin{equation}
  B = \kappaZ^5 \frac{
    \frac{\chi-1}{24\eta} - h_\sigma \frac{(\kappaO-2
      g_\sigma)(\kappaI^2 + 4 \kappaI + 6)}{\kappaI^4}
    - h_\sigma\frac{\kappaO^2 + 2\kappaO + 2}{\kappaO}
  }{2 \kappaZ^2 + 12 \kappaZ + 24}
\end{equation}
\begin{equation}
  \chi = \frac{(1-\eta)^4}{\eta^4 - 4\eta^3 + 4\eta^2 + 4\eta + 1}
\end{equation}
\newcommand\nastyetacuberoot{\sqrt[3]{54 g_\sigma^2 -
    6\sqrt{81g_\sigma^4 - 6g_\sigma^3}}}
\begin{equation}
  \eta = 1 - \frac{1}{\nastyetacuberoot} - \frac{\nastyetacuberoot}{6g_\sigma}
\end{equation}
\davidsays{The above is a sketch of how we might want to write our
  equations.  I think it matches up with the python now.  Below is the
old (presumably wrong) version.}

\begin{multline}
  h(r,g_\sigma) = 1 + h_\sigma e^{-\kappaO z} \\
  + h_\sigma(\kappaO - 2 g_\sigma) \xi e^{-\kappaI \xi} \\
  + \frac{\frac{(1-\eta)^4}{1+4\eta + 4\eta^2 - 4\eta^3 +
      \eta^4}\frac{1}{n}
    - I_0  -I_1(\kappaO - g_\sigma)}{I_2} z^2e^{-\kappaZ z}
\end{multline}
\begin{equation}
  I_0 = \frac{4\pi h_\sigma (2 + \sigma \kappaO (2 + \sigma \kappaO))}{\kappaO^3}
  - \frac{4\pi}{3} \sigma^3
\end{equation}
\begin{equation}
  I_1 = \frac{4\pi h_\sigma (6 + \sigma \kappaI (4 + \sigma \kappaI))}{\kappaI^4}
\end{equation}
\begin{equation}
  I_2 = \frac{8\pi (12 + \sigma \kappaZ (6 + \sigma \kappaZ))}{\kappaZ^5}
\end{equation}
\begin{equation}
  z = r - \sigma
\end{equation}
\davidsays{Can someone check the above equations for correctness
  against the python code, in plot-ghs2.py.  We'll want to
  ensure the C++ code agrees with this as well.}
\fixme{Clean up the above equations, if possible.}
This function includes three fitted parameters, $\kappaO$, $\kappaI$,
and $\kappaZ$, which are given in Table~\ref{tab:fit-parameters}.
The fit is displayed in Fig.~\ref{fig:radial-distribution}.  In that
figure, it is apparent that the integral f $h(r)$ from
Eq.~\ref{eq:total-constraint} results in cancelling errors at large
distances.  The maximum error in $g(r)$ at packing fractions up to
0.4 is \maxerr, which occurs at $\eta = \etamaxerr$ and $r =
\rmaxerr$.

\begin{table}
  \begin{align*}
    \kappaO &= \kappazero \\
    \kappaI &= \kappaone \\
    \kappaZ &= \kappatwo
  \end{align*}
  \caption{Fit parameters \fixme{... put them here and format this nicely}\fixme{add dimensions here}}
  \label{tab:fit-parameters}
\end{table}
